---
title: "Model"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(psysds364data)
library(dplyr)
library(feather)
library(nlme)
library(dyadr)
library(mosaic)
```

```{r}
data(Goldberg)
data(Goldberg_rutendo)
```


```{r}
Goldberg_rutendo$group <- as_factor(Goldberg_rutendo$group)
levels(Goldberg_rutendo$group) <- c("les", "gay", "het")

Goldberg_rutendo <-  Goldberg_rutendo %>%
  filter((Member_A == 1 & Member_P == 2)|(Member_A == 2 & Member_P == 1))

var_labels <- data.frame(column_name = colnames(Goldberg_rutendo),
variable_label = sjlabelled::get_label(Goldberg_rutendo))
var_labels[grep("anxiety", var_labels$variable_label),]
```

### restructuring 

```{r}
Goldberg_yifan <- Goldberg_rutendo %>%
 dplyr::select(FamID, sexor, group, contains("Member"), contains("love"), contains("cnflct"), contains("ambiv"), contains("maint"), contains("seq"), contains("attach"), contains("feel"))
  
#%>%
  #mutate(id = row_number())

sub_G <- Goldberg_yifan[c(1:5, 6:656)]

sub_G$FeelMC_A <- NULL
sub_G$FeelMC_P <- NULL
#ppp: person, period, pairwise

Goldberg_ppp <- 
  unite(sub_G, "F_S_G_A_P", 1:5, sep = "_") %>%
  gather("key","value", 2:650) %>%
  separate(key, into = c("wave","scale"), sep = 3) %>%
  spread("scale", "value") %>%
  separate(F_S_G_A_P, into = c( "FamID", "sexor","group","Member_A","Member_P"), sep = "_") 

```

### MLM for wave 3
```{r}
ppp_3 <- Goldberg_ppp %>%
  filter(wave == "w13")


mlm <- gls(attach_A ~ relevel(group, ref = "het"), 
           data = ppp_3,
           correlation = corCompSymm(form=~1|FamID),
           na.action = na.omit)

summary(mlm)


apim_in <- gls(attach_A ~ love_A + love_P ,
               data = ppp_3,
               correlation = corCompSymm(form=~1|FamID),
               na.action = na.omit)

summary(apim_in)
```

### longitudinal 
# Growth Curve modeling 

covariance between slope and intercept 
optional: time stamp for each dyad 

relationship, pick love 

replace gender with as.factor (member)

```{r}

Goldberg_ppp$FamID <- as.numeric(Goldberg_ppp$FamID)

# rescaling the time
Goldberg_ppp_c <- Goldberg_ppp %>%
  mutate(time = ifelse(wave == "w11",-1, ifelse(wave == "w12",0,ifelse(wave == "w13",1,ifelse(wave == "w14",2,NA)))),
         obsid = time + 3*(FamID-1),
         month = ifelse(time == -1, 0, ifelse(time == 0, 3, ifelse(time == 1, 12, ifelse(time == 2, 24, NA)))))

```



```{r}
Goldberg_ppp_c$time <-  as.numeric(Goldberg_ppp_c$time)

ctrl <- lmeControl(msMaxIter=10000,
                   MaxIter=100000,
                   msMaxEval=10000,
                   returnObject=TRUE,
                   niterEM=10000,
                   nlmStepMax=1000)

dyad <- lme(attach_A ~ time + love_A,
                      data = Goldberg_ppp_c, 
                      random = ~ Member_A + Member_A:time  - 1|FamID,
                      correlation = corCompSymm(form = ~1|FamID/obsid),
                      weights = varIdent(form = ~1|Member_A),
                      na.action = na.omit,
                      control = ctrl)



summary(dyad)

```


```{r}
options(scipen=999)
Goldberg_ppp_c <- Goldberg_ppp_c %>%
  mutate(I1 = ifelse(Member_A == 1, 1, 0),
         I2 = ifelse(Member_A == 2, 1, 0),
         I_sum = I1 + I2, 
         I_diff = I1 - I2, 
         TIME_sum = time*I_sum, 
         TIME_diff = time*I_diff)

```

```{r}
full_model <- lme(attach_A ~  time + love_A + love_P + group + feel_A + feel_P + seq_A + seq_P,
                        data = Goldberg_ppp_c, 
                        random = list(FamID = pdBlocked(list(~ I_sum+TIME_sum-1,~ I_diff+TIME_diff-1))),
                        correlation = corCompSymm(form = ~1|FamID/obsid),
                        na.action = na.omit)

full_model_results=summary(full_model)
full_model_results

#ran full model found that only anxiety was significant

reduced_model <- lme(attach_A ~  time + seq_A ,
                        data = Goldberg_ppp_c, 
                        random = list(FamID = pdBlocked(list(~ I_sum+TIME_sum-1,~ I_diff+TIME_diff-1))),
                        correlation = corCompSymm(form = ~1|FamID/obsid),
                        na.action = na.omit)

reduced_model_results=summary(reduced_model)
reduced_model_results
#reduced model with time and anxiety
#write about that anxiety at timepoint x is significant predictor for attachment at timepoint x



```

our anxiety at this wave is related to attachment at that wave

times * anxiety related to attachment 


mediation test
```{r}
#testing for mediation to see if anxiety mediates love in predicting for attachment

###Step 1: Estimating and testing the total effect (c) of love  (X) on attachment (Y)
###Step 1: Estimating and testing the total effect (c) of Other Positivity (X) on Satisfaction (Y)
stp1 <- lme(attach_A ~  time + love_A + love_P,
                        data = Goldberg_ppp_c, 
                        random = list(FamID = pdBlocked(list(~ I_sum+TIME_sum-1,~ I_diff+TIME_diff-1))),
                        correlation = corCompSymm(form = ~1|FamID/obsid),
                        na.action = na.omit)

stp1_results=summary(stp1)


###Step 2: Testing the effects of the love (X) on the mediators of anxiety member a meber b (M).
stp2 <- lme(seq_A ~  time + love_A + love_P,
                        data = Goldberg_ppp_c, 
                        random = list(FamID = pdBlocked(list(~ I_sum+TIME_sum-1,~ I_diff+TIME_diff-1))),
                        correlation = corCompSymm(form = ~1|FamID/obsid),
                        na.action = na.omit)

stp2_results=summary(stp2)

stp3 <- lme(attach_A ~  time + love_A + love_P + seq_A + seq_P,
                        data = Goldberg_ppp_c, 
                        random = list(FamID = pdBlocked(list(~ I_sum+TIME_sum-1,~ I_diff+TIME_diff-1))),
                        correlation = corCompSymm(form = ~1|FamID/obsid),
                        na.action = na.omit)

stp3_results=summary(stp3)



#Function that returns mcmc CI. 
mcmamCI <- function(aval, bval, varA, varB, n){

#code (Selig & Preacher, 2008).
  require(MASS)
  
  a=aval
  b=bval
  rep=n
  conf=95
  pest=c(a,b)
  acov <- matrix(c(varA, 0, 0, varB),2,2)

  mcmc <- mvrnorm(rep,pest,acov,empirical=FALSE)

  ab <- mcmc[,1]*mcmc[,2]

  low=(1-conf/100)/2
  upp=((1-conf/100)/2)+(conf/100)

  LL=quantile(ab,low)
  UL=quantile(ab,upp)
  LL=format(LL,digits=3)
  UL=format(UL,digits=3)

  CI <- cbind.data.frame(LL, UL)
  return(CI)

}

act_H_a <- coef(summary(stp2))[3,1]
act_H_a_se <- coef(summary(stp2))[3,2]
act_H_b <- coef(summary(stp3))[3,1]
act_H_b_se <- coef(summary(stp3))[3,2]

mcmamCI(act_H_a, act_H_b, act_H_a_se^2, act_H_b_se^2, 3000)
```



```{r}
## number stuff
intvari=as.numeric(VarCorr(reduced_model_results)[1,1])+as.numeric(VarCorr(reduced_model_results)[3,1]) 
intcovari=as.numeric(VarCorr(reduced_model_results)[1,1])-as.numeric(VarCorr(reduced_model_results)[3,1])
slovari=as.numeric(VarCorr(reduced_model_results)[2,1])+as.numeric(VarCorr(reduced_model_results)[4,1]) 
slocovari=as.numeric(VarCorr(reduced_model_results)[2,1])-as.numeric(VarCorr(reduced_model_results)[4,1])

intslow= as.numeric(getVarCov(reduced_model_results)[2,1])+as.numeric(getVarCov(reduced_model_results)[4,3])
intslob= as.numeric(getVarCov(reduced_model_results)[2,1])-as.numeric(getVarCov(reduced_model_results)[4,3])
```

The intercept variance: `r round(intvari,6)`  
The intercept covariance: `r round(intcovari,6)`  
Correlation between intercepts: `r round(intcovari/intvari,6)`  
The slope variance: `r round(slovari,6)`  
The slope covariance: `r round(slocovari,6)`  
Correlation between the slopes: `r round(slocovari/slovari,6)`  
Slope-intercept covariance (within a person): `r round(as.numeric(intslow),6)`    
Slope-intercept correlation (within a person): `r round(intslow/sqrt(intvari*slovari),6)` 
Slope-intercept covariance (between persons): `r round(as.numeric(intslob),6)`  
Slope-intercept correlation (between a person): `r round(intslob/sqrt(intvari*slovari),6)` 

The intercept variance: 0.417106
The intercept covariance: 0.217243
Correlation between intercepts: 0.520834
The slope variance: 0.041305
The slope covariance: 0.0218
Correlation between the slopes: 0.527776
Slope-intercept covariance (within a person): 0.045754
Slope-intercept correlation (within a person): 0.348584 Slope-intercept covariance (between persons): 0.02253
Slope-intercept correlation (between a person): 0.171648