---
title: "importData"
author: "Karen Santamaria"
date: "9/23/2019"
output: html_document
---

```{r setup}
library(tidyverse)
library(devtools)
library(papaja)
library(psysds364data)
library(plyr)
```

```{r}
data("Goldberg")
data("Goldberg_rutendo")
<<<<<<< HEAD
```

=======
>>>>>>> 48c5a5c9547b970eee98ba496190c0f2be6b62de

Goldberg_rutendo <- Goldberg_rutendo %>%
  filter((Member_A == 1 & Member_P == 2) | (Member_A == 2 & Member_P == 1)) 

Goldberg_yifan <- Goldberg_rutendo %>%
 select(FamID, sexor, group, contains("Member"), contains("love"), contains("cnflct"), contains("ambiv"), contains("maint"), contains("seq"), contains("attach"), contains("feel"))
```


Create ppp table
```{r}
sub_G <- Goldberg_yifan[c(1:5, 6:656)]

sub_G$FeelMC_A <- NULL
sub_G$FeelMC_P <- NULL

Goldberg_ppp <- 
  unite(sub_G, "F_S_G_A_P", 1:5, sep = "_") %>%
  gather("key","value", 2:650) %>%
  separate(key, into = c("wave","scale"), sep = 3) %>%
  spread("scale", "value") %>%
  separate(F_S_G_A_P, into = c( "FamID", "sexor","group","Member_A","Member_P"), sep = "_") 

```


Search through variables for information
```{r}
Goldberg_rutendo%>%
  select(contains('love')) %>%
  names()

var_labels <- data.frame(column_name = colnames(Goldberg_),
variable_label = sjlabelled::get_label(Goldberg))
var_labels[grep("rel", var_labels$variable_label),]
```



Demographic variables as factors to make easier to use
w11FamInc_A
```{r}
Goldberg_rutendo$w11Race_A <- as_factor(Goldberg_rutendo$w11Race_A)
Goldberg_rutendo$w12Race_A <- as_factor(Goldberg_rutendo$w12Race_A)
Goldberg_rutendo$group <- as_factor(Goldberg_rutendo$group)
Goldberg_rutendo$sexor <- as_factor(Goldberg_rutendo$sexor)
Goldberg_rutendo$w11Educ_A <- as_factor(Goldberg_rutendo$w11Educ_A)
Goldberg_rutendo$w11Couple_A <- as_factor(Goldberg_rutendo$w11Couple_A)
Goldberg_rutendo$w11WhyAdopt_A <- as_factor(Goldberg_rutendo$w11WhyAdopt_A)
Goldberg_rutendo$gender_A <- as_factor(Goldberg_rutendo$gender_A)
```


participant age??? educations ask randi cant find

income, age of children,


percentages of gender
```{r}
Goldberg_perc_gender <- Goldberg_rutendo %>%
  filter((Member_A == 1 & Member_P == 2) | (Member_A == 2 & Member_P == 1)) %>%
  group_by(gender_A) %>%
  tally  %>%
  mutate(percent=100* (n/sum(n)))  %>%
  arrange(desc(percent))
Goldberg_perc_gender
```

percentages of racial groups
```{r}
Goldberg_perc_race <- Goldberg_rutendo %>%
  filter((Member_A == 1 & Member_P == 2) | (Member_A == 2 & Member_P == 1)) %>%
  group_by(w12Race_A) %>%
  tally  %>%
  mutate(percent=100* (n/sum(n))) %>%
  select(-n) %>%
  arrange(desc(percent))
Goldberg_perc_race
```

percentages of educations
```{r}
Goldberg_perc_edu <- Goldberg_rutendo %>%
  group_by(w11Educ_A) %>%
  tally  %>%
  mutate(percent=100* (n/sum(n))) %>%
  arrange(desc(percent))
Goldberg_perc_edu
```

income family
```{r}
summary(Goldberg_rutendo$w11FamInc_A)
summary(Goldberg_rutendo$w14FamInc_A)
```

income personal
```{r}
summary(Goldberg_rutendo$w11PersInc_A)
summary(Goldberg_rutendo$w14PersInc_A)
```

Age of child when came to be with you, in months
```{r}
summary(Goldberg_rutendo$w12Age_A)
```


age of children
```{r}
summary(Goldberg_rutendo$w14CBCLage_A)
```

perc orientations
```{r}
Golberg_perc_orientation <- Goldberg_rutendo %>%
  group_by(sexor) %>%
  tally  %>%
  mutate(percent=100* (n/sum(n))) %>%
  arrange(desc(percent))
Golberg_perc_orientation
```


other
```{r}
Goldberg_perc_adopt_type <- Goldberg_rutendo %>%
  group_by(w11Couple_A) %>%
  tally  %>%
  mutate(percent=100* (n/sum(n)))  %>%
  arrange(desc(percent))
Goldberg_perc_adopt_type

Goldberg_perc_adopt_why <- Goldberg_rutendo %>%
  group_by(w11WhyAdopt_A) %>%
  tally  %>%
  mutate(percent=100* (n/sum(n)))  %>%
  arrange(desc(percent))
Goldberg_perc_adopt_why
```





report the number of same-gender and different-gender couples. 
```{r}
Golberg_perc_relation <- Goldberg_rutendo %>%
  group_by(group) %>%
  tally  %>%
  mutate(percent=100* (n/sum(n))) %>%
  arrange(desc(percent))
Golberg_perc_relation
```




report the number of same-race and different-race dyads
```{r}
Goldberg_rutendo %>%
  filter(Member_A == 1 & Member_P == 2) %>%
  mutate(w12POC_P = if_else(w12Race_P == 'Caucasian' | 
                            w12Race_P == 'Mostly Caucasian (1/8 American Indian)' | 
                            w12Race_P == 'Mostly white', 'white','poc')) %>%
  mutate(w12POC_A = if_else(w12Race_A == 'Caucasian' |
                            w12Race_A == 'Mostly Caucasian (1/8 American Indian)' |
                            w12Race_A == 'Mostly white', 'white','poc' )) %>%
  group_by(w12POC_A,w12POC_P) %>%
  tally %>%
  mutate(percent=100* (n/141)) %>%
  arrange(desc(percent))


Goldberg_rutendo %>%
  filter(Member_A == 1 & Member_P == 2) %>%
  group_by(w12Race_A,w12Race_P) %>%
  tally  %>%
  mutate(percent=100*n/141)  %>%
  arrange(desc(percent))
```

Report samplesize(number of individuals as well as number ofdyads)
```{r}
#get num or rows
```




filter out so a single couple shows 

relationship length different between les, het, gay male couples? anova test
```{r}
fit <- aov(w11RelDur_A ~ group, data=Goldberg_rutendo) 
layout(matrix(c(1,2,3,4),2,2))
plot(fit) 


ggplot(Goldberg_rutendo, aes(x=group, y=w11RelDur_A, fill=group)) + 
  geom_boxplot() 
```

fam income different between les, het, gay male couples? anova test
```{r}
fit <- aov(w11FamInc_A ~ group, data=Goldberg_rutendo) 
layout(matrix(c(1,2,3,4),2,2)) 
plot(fit) 
anova(fit)

ggplot(Goldberg_rutendo, aes(x=group, y=w11RelDur_A, fill=group)) + 
  geom_boxplot() 
```




